---
title: "Assignment 3"
author: "Isabel Hojman"
date: "15/11/2017"
output: html_document
---

# Exercise 1

```{r}
`%>%` <- magrittr::`%>%`
#library(dplyr)
```

## Task A

```{r}
#print(stressshift::stress_shift_unamb)
stress_shift_3dict <- dplyr::filter(stressshift::stress_shift_unamb, Dict %in% c("W1802", "J1917", "C1687")) 
print(stress_shift_3dict)
print(dim(stress_shift_3dict))
```


## Task B

```{r}
stress_shift_3dict_using_pipe <- stressshift::stress_shift_unamb %>% dplyr::filter(Dict %in% c("W1802", "J1917", "C1687"))
identical(stress_shift_3dict, stress_shift_3dict_using_pipe)
```

## Task C

```{r}
stress_shift_3dict_nouns <- stress_shift_3dict %>% dplyr::filter(Category == "Noun")
#print(stress_shift_3dict_nouns)
stress_shift_3dict_verbs <- stress_shift_3dict %>% dplyr::filter(Category == "Verb")
#print(stress_shift_3dict_verbs)
stress_shift_3dict_using_bind <- dplyr::bind_rows(stress_shift_3dict_nouns, stress_shift_3dict_verbs)
#print(stress_shift_3dict_using_bind)
stress_shift_3dict_using_bind_reversed <- dplyr::bind_rows(stress_shift_3dict_verbs, stress_shift_3dict_nouns)
#print(stress_shift_3dict_using_bind_reversed)
identical(stress_shift_3dict, stress_shift_3dict_using_bind)
identical(stress_shift_3dict, stress_shift_3dict_using_bind_reversed)
```


## Task D

```{r}
stress_shift_nouns_renamed <- stressshift::stress_shift_unamb %>% 
  dplyr::filter(Category == "Noun") %>%
  dplyr::select(Word, Dict, Syllable) %>%
  dplyr::rename(Syllable_Noun = Syllable)
#print(stress_shift_nouns_renamed)

stress_shift_verbs_renamed <- stressshift::stress_shift_unamb %>% 
  dplyr::filter(Category == "Verb") %>%
  dplyr::select(Word, Dict, Syllable) %>%
  dplyr::rename(Syllable_Verb = Syllable)
#print(stress_shift_verbs_renamed)

stress_shift_wide <- dplyr::inner_join(stress_shift_nouns_renamed, stress_shift_verbs_renamed)
print(stress_shift_wide)
```

inner_join(x, y) "return all rows from x where there are matching values in y, and all columns from x and y. If there are multiple matches between x and y, all combination of the matches are returned." Therefore, it only returns the rows that are shared by both tables. That's the reason why it has fewer rows than the original tables.

## Task E

```{r}
ggplot2::ggplot(stressshift::stress_shift_unamb, ggplot2::aes(x=Category, fill=Syllable)) +
ggplot2::geom_bar(position="dodge", colour="black") + ggplot2::scale_fill_brewer(palette="Set3")
```

## Task F


```{r}
stress_shift_byword <- stress_shift_wide %>%
  dplyr::group_by(Word) %>%
  dplyr::summarise(Noun_Percent_Syll_1 = (sum(Syllable_Noun =="Syllable 1"))/n(),
                   Verb_Percent_Syll_1 = (sum(Syllable_Verb =="Syllable 1"))/n())
#print(stress_shift_byword)
print(dim(stress_shift_byword))
```


## Task G

```{r}
ggplot2::ggplot(stress_shift_byword, ggplot2::aes(x=Noun_Percent_Syll_1, y=Verb_Percent_Syll_1)) + ggplot2::geom_point()
```


## Task H


```{r}

```



























