---
title: "Assignment 3"
author: "Isabel Hojman"
date: "15/11/2017"
output: html_document
---

```{r}
source("Functions.R")
```

# Exercise 1

```{r}
`%>%` <- magrittr::`%>%`
#library(dplyr)
```

## Task A

```{r}
#print(stressshift::stress_shift_unamb)
stress_shift_3dict <- dplyr::filter(stressshift::stress_shift_unamb, Dict %in% c("W1802", "J1917", "C1687")) 
print(stress_shift_3dict)
print(dim(stress_shift_3dict))
```


## Task B

```{r}
stress_shift_3dict_using_pipe <- stressshift::stress_shift_unamb %>% dplyr::filter(Dict %in% c("W1802", "J1917", "C1687"))
identical(stress_shift_3dict, stress_shift_3dict_using_pipe)
```

## Task C

```{r}
stress_shift_3dict_nouns <- stress_shift_3dict %>% dplyr::filter(Category == "Noun")
#print(stress_shift_3dict_nouns)
stress_shift_3dict_verbs <- stress_shift_3dict %>% dplyr::filter(Category == "Verb")
#print(stress_shift_3dict_verbs)
stress_shift_3dict_using_bind <- dplyr::bind_rows(stress_shift_3dict_nouns, stress_shift_3dict_verbs)
#print(stress_shift_3dict_using_bind)
stress_shift_3dict_using_bind_reversed <- dplyr::bind_rows(stress_shift_3dict_verbs, stress_shift_3dict_nouns)
#print(stress_shift_3dict_using_bind_reversed)
identical(stress_shift_3dict, stress_shift_3dict_using_bind)
identical(stress_shift_3dict, stress_shift_3dict_using_bind_reversed)
```


## Task D

```{r}
stress_shift_nouns_renamed <- stressshift::stress_shift_unamb %>% 
  dplyr::filter(Category == "Noun") %>%
  dplyr::select(Word, Dict, Syllable) %>%
  dplyr::rename(Syllable_Noun = Syllable)
#print(stress_shift_nouns_renamed)

stress_shift_verbs_renamed <- stressshift::stress_shift_unamb %>% 
  dplyr::filter(Category == "Verb") %>%
  dplyr::select(Word, Dict, Syllable) %>%
  dplyr::rename(Syllable_Verb = Syllable)
#print(stress_shift_verbs_renamed)

stress_shift_wide <- dplyr::inner_join(stress_shift_nouns_renamed, stress_shift_verbs_renamed)
print(stress_shift_wide)
```

inner_join(x, y) "return all rows from x where there are matching values in y, and all columns from x and y. If there are multiple matches between x and y, all combination of the matches are returned." Therefore, it only returns the rows that are shared by both tables. That's the reason why it has fewer rows than the original tables.

## Task E

```{r}
ggplot2::ggplot(stressshift::stress_shift_unamb, ggplot2::aes(x=Category, fill=Syllable)) +
ggplot2::geom_bar(position="dodge", colour="black") + ggplot2::scale_fill_brewer(palette="Set3")
```

## Task F


```{r}
stress_shift_byword <- stress_shift_wide %>%
  dplyr::group_by(Word) %>%
  dplyr::summarise(Noun_Percent_Syll_1 = (sum(Syllable_Noun =="Syllable 1"))/n(),
                   Verb_Percent_Syll_1 = (sum(Syllable_Verb =="Syllable 1"))/n())
#print(stress_shift_byword)
print(dim(stress_shift_byword))
```


## Task G

```{r}
ggplot2::ggplot(stress_shift_byword, ggplot2::aes(x=Noun_Percent_Syll_1, y=Verb_Percent_Syll_1)) + ggplot2::geom_point()
```


## Task H


```{r}
stress_shift_nouns_renamed <- stressshift::stress_shift_unamb %>% 
  dplyr::filter(Category == "Noun") %>%
  dplyr::select(Word, Dict, Syllable) %>%
  dplyr::rename(Syllable_Noun = Syllable)
#print(stress_shift_nouns_renamed)

stress_shift_verbs_renamed <- stressshift::stress_shift_unamb %>% 
  dplyr::filter(Category == "Verb") %>%
  dplyr::select(Word, Dict, Syllable) %>%
  dplyr::rename(Syllable_Verb = Syllable)
#print(stress_shift_verbs_renamed)

stress_shift_wide_all <- dplyr::left_join(stress_shift_nouns_renamed, stress_shift_verbs_renamed)
#print(dim(stress_shift_wide_all)) 

stress_shift_byword_all <- stress_shift_wide_all %>%
  dplyr::group_by(Word) %>%
  dplyr::summarise(Noun_Percent_Syll_1 = (sum(Syllable_Noun =="Syllable 1"))/n(),
                   Verb_Percent_Syll_1 = (sum(Syllable_Verb =="Syllable 1"))/n())
print(stress_shift_byword_all)
print(dim(stress_shift_byword_all))
```


# Excercise 2

## Task A

Insert a chunk that uses this function to calculate the observed value of the test statistic. If you use "Syllable 1" as the target value, with nouns as group 1 and verbs as group 2, the result should be `0.6839201`.

```{r}
dif <- difference_in_proportion(stressshift::stress_shift_unamb, "Syllable", "Category", "Noun", "Verb", "Syllable 1")
print(dif)
```


## Task B

```{r}
if(!exists(".Random.seed")) set.seed(NULL)
previous_seed <- .Random.seed
set.seed(1)
ptest_stress <- permutation_twogroups(stressshift::stress_shift_unamb,
                      "Syllable", "Category", "Noun", "Verb",
                      difference_in_proportion,
                      n_samples=99,
                      "Syllable 1")
set.seed(previous_seed)
permutation_pvalue_right(ptest_stress)
```

Make a histogram of the resulting test statistics with a vertical line indicating the value of the observed test statistic. Use a bin width of 0.005 so that you can see something in the histogram (otherwise it's not going to have many bars).

```{r}
ptest_st <- tibble::as_tibble(ptest_stress["permuted"])
p <- ggplot2::ggplot(ptest_st, ggplot2::aes_string(x="permuted")) +
  ggplot2::geom_histogram(colour="black", fill="firebrick", binwidth=0.005) +
  ggplot2::geom_vline(ggplot2::aes(xintercept=ptest_stress[["observed"]]), color="firebrick") +
  ggplot2::ggtitle("Permutation Noun-Verb Syllable 1")

print(p)
```

# Exercice 3


## Task A



```{r}
S1_Noun_prop <- stressshift::stress_shift_unamb %>% 
  dplyr::filter(Category == "Noun") %>% 
  dplyr::summarise(size=sum(n()), prop=length(which(Syllable =="Syllable 1"))/(n()))

S1_Verb_prop <- stressshift::stress_shift_unamb %>% 
  dplyr::filter(Category == "Verb") %>% 
  dplyr::summarise(size=sum(n()), prop=length(which(Syllable =="Syllable 1"))/(n()))

print(S1_Noun_prop)
print(S1_Verb_prop)
```

Add columns `Noun_Percent_Syll_1` and `Verb_Percent_Syll_1` with the appropriate relative frequencies for each replication. And add a column `Replication` containing `"R0001"`, `"R0002"`, ...,  as unique identifiers for each replication, which you can generate using the following code:

```{r}
Noun_N_Syll_1 <- rbinom(1000, S1_Noun_prop[["size"]], S1_Noun_prop[["prop"]])
Verb_N_Syll_1 <- rbinom(1000, S1_Verb_prop[["size"]], S1_Verb_prop[["prop"]])
stress_shift_replications <- tibble::data_frame(Noun_N_Syll_1=Noun_N_Syll_1, Verb_N_Syll_1=Verb_N_Syll_1)
#print(stress_shift_replications)
Replication <- paste0("R", sprintf("%04d", 1:1000))
#print(Replication)
stress_shift_replications <- tibble::add_column(stress_shift_replications, Replication = Replication)
print(stress_shift_replications)

```



Finally, add a column called `Difference_in_Proportion` giving the value of the test statistic from before. You don't need to try to use your existing function. (That would be hard and pointless.) You just need to calculate the difference in the two proportions, noun minus verb.

Make a histogram for this new distribution of test statistics, again with a vertical line at the observed value in the original data, plotting again with a bin width of 0.005—but change the $x$ limits of the graph by adding the following to the plot object:

```
ggplot2::xlim(c(-0.1, 0.8))
```

Now re-plot your test statistic distribution obtained using the permutation test, immediately below this new plot, with the same $x$ limits.

Explain what these two histograms are showing. Relate the location of the vertical line to the result on page 57 of the Good textbook about the expected value of a binomial distribution.


## Task B




## Task C





# Exercice 4


















